---
title: "Homework 1"
output: github_document
---

# Problem 1

Create a data frame and take means of each variable.
```{r message=FALSE}
library(tidyverse)

vec_numeric = rnorm(8)
vec_logical = vec_numeric > 0
vec_char = c("1", "2", "3", "4", "5", "6", "7", "8")
vec_factor = factor(c("low", "high", "medium", "high",  "low", "medium", "high", "low"))

df = tibble(vec_numeric, vec_logical, vec_char, vec_factor)

mean(vec_numeric)
mean(vec_logical)
mean(vec_char)
mean(vec_factor)

```

I can take the mean of _numeric_ and _logical_ variable but cannot do this to _factor_ and _character_.

```{r eval=FALSE}
as.numeric(vec_logical)
as.numeric(vec_char)
as.numeric(vec_factor)
```

`as.numeric` function transfers all the variables to numeric.??????

Calulation.

```{r}
as.numeric(vec_logical) * vec_numeric
as.factor(vec_logical) * vec_numeric
as.numeric(as.factor(vec_logical)) * vec_numeric
```



# Problem 2

```{r}
x = rnorm(500)
y = rnorm(500)
vec_logical2 = x + y > 1
vec_numeric2 = as.numeric(vec_logical2)
vec_factor2 = as.factor(vec_logical2)

df2 = tibble(x, y, vec_logical2, vec_numeric2, vec_factor2)

df2
```

A short description of my vector:

*  There are `r nrow(df2)` rows and `r ncol(df2)` columes.

*  The mean of x is `r mean(x)`. The median of x is `r median(x)`. The standard deviation of x is `r sd(x)`.

*  The proportion of cases for which x+y>1 is `r  sum(as.numeric(vec_logical2)) / 500`.

```{r}
ggplot(df2, aes(x = x, y = y, color = vec_logical2)) + geom_point()
ggplot(df2, aes(x = x, y = y, color = vec_factor2)) + geom_point()
ggplot(df2, aes(x = x, y = y, color = vec_numeric2)) + geom_point()


```


